---
title: "Assignment 3"
author: "Rachel Rineman"
date: "2/5/2022"
output: html_document
---

---
title: "Basic Functions in R- Pt 1"
author: "Rachel Rineman
date: "1/30/2022"
output: html_document
---
For your first R Assignment, complete the questions below. Remember, weekly assignments are graded based on attempts, so it's ok if you don't get everything immediately. Please submit your answers by 1) updating this file in your GitHub repository and 2) uploading a .html file of the assignment to this repository. 

1. Create a vector called score that contains every 9th number between 1 and 100. 
```{r}
score <- seq(1,100, by =9)
```

2. Create a vector called participants that contains the numbers 1-12.
```{r}
participants <- c(1:12)
```

3. Create a list called condition that repeats the words control and experimental six times. 
```{r}
rep("control", 6)
rep("experimental", 6)

condition <- c("control", "control", "control", "control", "control", "control",
"experimental", "experimental", "experimental", "experimental", "experimental",
"experimental")

```

4. Create a dataframe from the variables in #1-3. 
```{r}
dataCombine <- cbind.data.frame(score, participants, condition)
```

5. Take the mean of the score column.
```{r}
mean(score)
```

6. Open the mtcars dataframe. Print the dataframe.  
```{r}
mtcars
data("mtcars")
```

7. Create a subset of data for cars that have 6 cylinders (cyl column).
```{r}
sixCyl<- subset(mtcars, mtcars$cyl == 6)
sixCyl
```

8. Summarize this subset of data. 
```{r}
summary(sixCyl)
```

8. Create a dataframe that contains cars with higher than average miles per gallon (mpg). 
```{r}
mean(mtcars$mpg)
goodMPG<- subset(mtcars, mtcars$mpg >20.10)
goodMPG
```

9. How many cars are in this subset? 
There are 11 cars that have above average miles per gallon. 

10. Load the ggplot2 library
```{r}
library(ggplot2)
```

```{r}
View(diamonds)
```

11. Open the diamonds dataset. How do you know that you've loaded it?
The dataset opened in another tab and it shows in the global environment. 

12. Create a new dataframe that has diamonds greater than 1 carat and an ideal cut. 
```{r}
library(tidyverse)
oneCarat<- subset(diamonds, diamonds$carat >1)
onecaratIdealReal<- oneCarat %>% filter(cut == "Ideal")

```

13. Find the mean and standard deviation of price for this new dataset. 
```{r}
mean(onecaratIdealReal$price)
```
```{r}
sd(onecaratIdealReal$price)
```

14. Create another new dataframe that includes all diamonds with a price between $2500 and $5000. 
```{r}
library(ggplot2)
library(tidyverse)
library(tibble)
view(diamonds)
```

```{r}
subset(diamonds, diamonds$price(between(,2500,5000))
```

```{r}
filter(diamonds, between(diamonds$price, 2500, 5000))
```

```{r}
subset(diamonds, diamonds$price == 2500:5000)
```
I tried this is probably 20 different ways, but I could not figure it out. 

15. Which color occurs most in this subset? 
```{r}
library(modeest)
mode(onecaratIdealReal$color)
```
I thought maybe if I used mode, it would tell me the most common color (I used a subset that was successful in an earlier problem)
